---
title: "Example Progress Bar Output"
author: "Robert M Flight"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Progress Bars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r init, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

Load the package, and define the function that will use the progress bar.

```{r setup}
library(knitrProgressBar)
arduously_long_nchar <- function(input_var, .pb=NULL) {
  
  if ((!is.null(.pb)) && inherits(.pb, "Progress") && (.pb$i < .pb$n)) .pb$tick()$print()
  
  Sys.sleep(0.1)
  
  nchar(input_var)
  
}
```

## Normal Progress Bar

Will show up in the output document, but not in a terminal running `rmarkdown::render`.

```{r test_pb}
pb <- progress_estimated(length(letters))

purrr::map_int(letters, arduously_long_nchar, .pb = pb)
```

## Using stderr()

This one will show up in the terminal when running `rmarkdown::render`.

```{r test_pb_stderr}
pb <- progress_estimated(length(letters), write_location = stderr())

purrr::map_int(letters, arduously_long_nchar, .pb = pb)
```

## Using a file

This one will instead write to a file, and can be watched by `tailf` for example
in a linux-alike.

```{r test_pb_file}
log_loc <- file.path(getwd(), "test.log")
pb <- progress_estimated(length(letters), write_location = log_loc)

purrr::map_int(letters, arduously_long_nchar, .pb = pb)
```

We can see that the progress was written to the file by displaying the file contents:

```{r view_file}
readLines(log_loc)
```

```{r delete_testlog, include = FALSE}
file.remove(log_loc)
```

## No Progress Bar

```{r test_pb_null}
pb <- progress_estimated(length(letters), write_location = NULL)

purrr::map_int(letters, arduously_long_nchar, .pb = pb)
```
